---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# increment

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->

> Non-Parametric Causal Effects Based on Incremental Propensity Score Interventions

## Installation

You can install increment from [GitHub](https://github.com/) with:

``` r
devtools::install_github("nt-williams/increment")
```

## Example 

```{r, eval = FALSE}
n <- 250
W <- matrix(rnorm(n*3), ncol=3)
A <- rbinom(n,1, 1/(1+exp(-(.2*W[,1] - .1*W[,2] + .4*W[,3]))))
Y <- A + 2*W[,1] + W[,3] + W[,2]^2 + rnorm(n)
ex <- data.frame(W, A, Y)

# sl3 learner stack
library(sl3)
lrnrs <- sl3::make_learner_stack(Lrnr_glm_fast, 
                                 Lrnr_ranger, 
                                 Lrnr_xgboost)

# increment function
increment(ex, "A", "Y", c("X1", "X2", "X3"), delta = seq(0.1, 5, length.out = 10), 
          outcome_type = "continuous", learners_outcome = lrnrs, learners_trt = lrnrs)
#> Incremental Z estimator
#> 
#>    increment  estimate std.error  conf.low conf.high
#> 1  0.1000000 0.9183776 0.3649177 0.2031389  1.633616
#> 2  0.6444444 1.2064158 0.1919722 0.8301502  1.582681
#> 3  1.1888889 1.3609284 0.1873993 0.9936257  1.728231
#> 4  1.7333333 1.4608922 0.2099085 1.0494716  1.872313
#> 5  2.2777778 1.5309389 0.2321637 1.0758981  1.985980
#> 6  2.8222222 1.5820198 0.2504068 1.0912225  2.072817
#> 7  3.3666667 1.6236070 0.2654183 1.1033871  2.143827
#> 8  3.9111111 1.6508011 0.2773495 1.1071960  2.194406
#> 9  4.4555556 1.6756341 0.2877440 1.1116559  2.239612
#> 10 5.0000000 1.7007632 0.2959063 1.1207869  2.280740
#> 
#> Reference
#> Nonparametric Causal Effects Based on Incremental Propensity Score Interventions (Kennedy, 2019)
```

## References

Edward H. Kennedy (2019) Nonparametric Causal Effects Based on Incremental Propensity Score Interventions, Journal of the American Statistical Association, 114:526, 645-656, DOI: 10.1080/01621459.2017.1422737

Kwangho Kim and Edward H. Kennedy and Ashley I. Naimi (2019) Incremental Intervention Effects in Studies with Many Timepoints, Repeated Outcomes, and Dropout, arXiv: 1907.04004
